On the use of decision trees to identify the local extrema in parallel global optimization algorithms

### 2023-02-01 2023/PAVT/ParallelDecisionTree.tex
Исправлены небольшие баги. Добавлена ссылка на рисунок.

@@

To demonstrate the efficiency of  investigated global search algorithm, here we present the results of  comparing this one with well known methods DIRECT and DIRECTl. Table \ref{tab:1} presents the averaged numbers of iterations executed by respective methods when  solving a series of GKLS problems. The sign ``>'' points to the situation when not all problems are  solved. In this case, the number of non-solved problems is given in brackets. As one can see,  GSA overcomes DIRECT and DIRECTl methods in average number of iterations necessary for solving the problems with the same precision.

\begin{table}[!ht]
    \caption{Averaged number of iterations}
    \label{tab:1}
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
        N & Problem class & DIRECT & DIRECTl & GSA  \\ \hline
        4 & Simple & >47282 (4) & 18983 & 11953  \\ \hline
        ~ & Hard & >95708 (7) & 68754 & 25263  \\ \hline
        5 & Simple & >16057 (1) & 16758 & 15920  \\ \hline
        ~ & Hard & >217215 (16) & >269064 (4) & >148342 (4)  \\ \hline
    \end{tabular}
\end{table}

>>>>

 Fig. (\ref{fig:fig1}) presents small example of how the algorithm works. Function contour plot are displayed, filled circles indicate successful steps, unfilled circles indicate unsuccessful steps in the investigating search.

@@

To demonstrate the efficiency of  investigated global search algorithm, here we present the results of  comparing this one with well known methods DIRECT and DIRECTl. Table \ref{tab:1} presents the averaged numbers of iterations executed by respective methods when  solving a series of GKLS problems. The sign `` $>$ '' points to the situation when not all problems are  solved. In this case, the number of non-solved problems is given in brackets. As one can see,  GSA overcomes DIRECT and DIRECTl methods in average number of iterations necessary for solving the problems with the same precision.

\begin{table}[!ht]
    \caption{Averaged number of iterations}
    \label{tab:1}
    \centering
    \begin{tabular}{|l|l|l|l|l|}
    \hline
        N & Problem class & DIRECT & DIRECTl & GSA  \\ \hline
        4 & Simple & $>47282 (4)$ & 18983 & 11953  \\ \hline
        ~ & Hard & $>95708 (7)$ & 68754 & 25263  \\ \hline
        5 & Simple & $>16057 (1)$ & 16758 & 15920  \\ \hline
        ~ & Hard & $>217215 (16)$ & $>269064 (4)$ & $>148342 (4)$  \\ \hline
    \end{tabular}
\end{table}
